The Tor Network - Design and Defenses \\ \Large Computer Security 1 - CS5460 \\ \LaTeX{}

### 2013-11-30 paper.tex
watermark attacks

\subsection{Malware attacks}

@@

\subsection{Compromising the exit node}

@@

\subsection{Cryptography Attacks}

@@

@@

The Tor developers responded to these and other similar article attacks, saying ``the good news is that they went for a browser exploit, meaning there's no indication they can break the Tor protocol or do traffic analysis on the Tor network. Infecting the laptop, phone, or desktop is still the easiest way to learn about the human behind the keyboard.'' and ``if you attack too many users, somebody's going to notice. So even if the NSA aims to surveil everyone, everywhere, they have to be a lot more selective about which Tor users they spy on. Just using Tor isn't enough to keep you safe in all cases.''. The developers also commented that the described attacks seemed ``relatively basic'' and ``out-of-date'', saying ``we still have a lot of work to do to make Tor both safe and usable, but we don't have any new work based on these slides''.\cite{TorBlogGuardian}

@@

The Tor Project responded to the Silk Road takedown with an analysis of the Tor network, saying ``So far, nothing about this case makes us think that there are new ways to compromise Tor (the software or the network). The FBI says that their suspect made mistakes in operational security, and was found through actual detective work.'' further saying that they found no evidence that the FBI broke into the webserver. They also reinforced their recommendations against providing public information online.\cite{TorBlogSilkRoad}

@@

@@

% http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=5962653
\bibitem{Ling2011}
  Zhen Ling
  \emph{Equal-Sized Cells Mean Equal-Sized Packets in Tor?}
  IEE International Conference on Communications, 2011

>>>>

\subsection{Malware}

@@

\subsection{Wiretapping the exit node}

@@

\subsection{Cryptographic Attacks}

@@

\subsection{Active Digital Watermarks}

Another potential method to de-anonymize users is through active watermarking of packets. Digital watermarks require less time deploy, often have a higher success rate, and do not require observing traffic for long periods of time. If an attacker can modify the traffic flow such that it is noticable at the other end of Tor, then it becomes easy to identify end users and correlate them with their activities.

In 2011, Zhen Ling \textit{et al} described an active watermark attack in which an attacker operates a reverse proxy and actively manipulates the size of the TCP packets transmitted to the exit node. Simultaneously, the attacker also runs a recovery method to detect the watermark on the user side. His watermark was a short sequence of 1s and 0s that could be encoded into the packet patterns. To transmit a 0, the attacker sends 498 bytes worth of web traffic to the Tor exit node, which is the exact size of the data portion of a Tor cell. Combined with the cell headers, the data packs into a single Tor cell of 512 bytes. To transmit a 1, the attacker sends 2444 bytes of data to the exit. The standard Maximum Transmission Unit (MTU) for Ethernet v2 lines is 1500 bytes and the TCP and IP headers are 20 and 32 bytes respectively, which means that a TCP packet can carry at most 1448 bytes of data. As the 2444 bytes from the attacker exceeds the MTU, two TCP packets are needed, one with a 1448-byte payload and the other with a 996-byte payload. The first TCP packet is received by the relay and is packed into three equally-sized cells, with padding added to the 452 bytes of the third cell. The second TCP packet becomes two cells of 498 bytes each, and thus the 2444 bytes becomes five Tor cells. Then these cells are processed, encoded as TCP packets, and retransmitted to the next relay. However, due to the design of cell queuing algorithms, TCP retransmission, and MTU restrictions, the two TCP packets may be split and combined into Tor cells in up to five different ways, each leaving a discernible packet signature. The attacker can then monitor the traffic near the client, examining the packet patterns generated by the attack. If the embedded signal is found, then it is quite likely that the traffic flows are correlated. In their tests, Zhen Ling \textit{et al} achieved a detection rate of nearly 90\%, with a false positive rate of less than 4\%, concluding that such an attack could degrade anonymity.\cite{Ling2011}

@@

The Tor developers responded to these and other related articles, saying ``the good news is that they went for a browser exploit, meaning there's no indication they can break the Tor protocol or do traffic analysis on the Tor network. Infecting the laptop, phone, or desktop is still the easiest way to learn about the human behind the keyboard.'' and ``if you attack too many users, somebody's going to notice. So even if the NSA aims to surveil everyone, everywhere, they have to be a lot more selective about which Tor users they spy on. Just using Tor isn't enough to keep you safe in all cases.''. The developers also commented that the described attacks seemed ``relatively basic'' and ``out-of-date'', saying ``we still have a lot of work to do to make Tor both safe and usable, but we don't have any new work based on these slides''.\cite{TorBlogGuardian}

@@

The Tor Project responded to the Silk Road takedown with an analysis of the Tor network, saying ``So far, nothing about this case makes us think that there are new ways to compromise Tor (the software or the network). The FBI says that their suspect made mistakes in operational security, and was found through actual detective work.'' further saying that they found no evidence that the FBI broke into the webserver. They also reinforced their recommendations against providing personal information online.\cite{TorBlogSilkRoad}

@@

Bauer and McCoy, \textit{et al}, described a low-resource routing attack against the Tor network.\cite{Bauer2007}

@@

% http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=5962653
\bibitem{Ling2011}
  Zhen Ling
  \emph{Equal-Sized Cells Mean Equal-Sized Packets in Tor?}
  IEEE International Conference on Communications, 2011
